### 2013-06-04 Publications/2013-TMI/03-introduction.tex
Added references
* Added reference to Greve et al (FreeSurfer) regarding Parcellation (close #86)
* Added reference to latest Alessandra's paper regarding structural connectivity analysis.

\section{Introduction}
\label{sec:introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
%
\IEEEPARstart{D}{iffusion} \gls{mri} is a widely used family
of \gls{mri} techniques \citep{sundgren_diffusion_2004} which recently 
has accounted for a growing interest in its application to structural 
connectivity analysis of the brain. This emerging field exploits
\gls{dwi} data to derive the local axonal structure at each imaging voxel 
\citep{basser_microstructural_2011} and estimate a whole-brain mapping of fiber 
tracts represented by trajectories reconstructed from the local information.
This comprehensive map of neural connections of the brain is called the 
\emph{connectome} \citep{hagmann_diffusion_2005,sporns_human_2005}. The connectome
analysis is a promising tool for neuroscience and clinical applications.
\todo[inline]{why? or references?}

Early \gls{dwi} research focused mainly on the improvements of imaging 
methodologies better understanding the diffusion effect and improving
image reconstruction methodologies. Currently, the connectome extraction 
and analysis relies on a large amount of sophisticated computational techniques
\citep{daducci_connectome_2012,hagmann_mr_2012} including acquisition,
reconstruction, modeling and model fitting, image processing, fibre tracking,
connectivity mapping, visualization, group studies, and inference. This 
growing complexity has given rise to challenging issues towards reliable 
structural information about the neuronal tracts \cite{johansen-berg_using_2009,
jones_white_2012,soares_hitchhikers_2013}, and statistical analysis 
\citep{meskaldji_comparing_????}. Here,we shall address three tasks included within 
the image processing stage in a unified approach: brain tissue segmentation in 
diffusion space (\autoref{sec:dwi_segmentation}), correction of geometrical 
distortions (\autoref{sec:distortion}), and structural image registration to 
diffusion coordinate space (\autoref{sec:registration}). These tasks are generally
solved independently, or combined in pairs. However, there exist fundamental 
coupling relationships that can be exploited to obtain a simultaneous solution to 
the three problems. This joint approach satisfactory impacts the downstream
outcomes of the whole pipeline with the increase of the internal consistency.

@@

The last addressed task in the image processing stage of the studied 
connectivity analysis pipelines is the structural information co-registration.
The need for this registration step is mainly raised when defining the 
nodes of the connectivity matrix. This definition step is named
\textit{cortical parcellation} as it imposes the regions that will be
considered to cluster the fiber bundles reaching the \gls{wm}-\gls{gm}
surface. The common procedure to accomplish this clustering is using
a predefined parcellation in a high-resolution structural T1-weighted 
atlas. The second goal that has justified the applicability of structural
images co-registration is susceptibility distortion correction
as discussed in \autoref{sec:distortion}. In any case, susceptibility 
distortion hinders a rigid-registration solution to this end.
Additionally, when applying non-linear intensity-based
registration algorithms other difficulties have to be addressed as
the significant \gls{pve} in the \gls{wm}-\gls{gm} layer, or the
inherent inadequacy of the B0 contrast (the only \textit{directionally
independent} existing in the raw \gls{dwi} data) due to the almost null
difference in intensity between \gls{wm} and \gls{gm} pixels. Early 
registration methods appeared targeting the distortion correction.
They quickly standardized the choice of T2 as anatomically correct source
to be registered against the B0 in \gls{dwi}. B0 images have a very similar
contrast to T2 weighted due to the duality of acquisition procedure. However,
parcellation is defined in T1 weighted space, adding an additional registration
step missing on the literature due to the novelty of the task. Even though this
registration step has a very low complexity compared to the remaining tasks of 
the pipeline process, it is one additional source of inconsistency and unreliability.

>>>>

\section{Introduction}
\label{sec:introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
%
\IEEEPARstart{D}{iffusion} \gls{mri} is a widely used family
of \gls{mri} techniques \citep{sundgren_diffusion_2004} which recently 
has accounted for a growing interest in its application to structural 
connectivity analysis of the brain. This emerging field exploits
\gls{dwi} data to derive the local axonal structure at each imaging voxel 
\citep{basser_microstructural_2011} and estimate a whole-brain mapping of fiber 
tracts represented by trajectories reconstructed from the local information.
This comprehensive map of neural connections of the brain is called the 
\emph{connectome} \citep{hagmann_diffusion_2005,sporns_human_2005}. The connectome
analysis is a promising tool for neuroscience and clinical applications
\citep{griffa_structural_2013}.

Early \gls{dwi} research focused mainly on the improvements of imaging 
methodologies better understanding the diffusion effect and improving
image reconstruction methodologies. Currently, the connectome extraction 
and analysis relies on a large amount of sophisticated computational techniques
\citep{daducci_connectome_2012,hagmann_mr_2012} including acquisition,
reconstruction, modeling and model fitting, image processing, fibre tracking,
connectivity mapping, visualization, group studies, and inference. This 
growing complexity has given rise to challenging issues towards reliable 
structural information about the neuronal tracts \cite{johansen-berg_using_2009,
jones_white_2012,soares_hitchhikers_2013}, and statistical analysis 
\citep{meskaldji_comparing_2013}. Here,we shall address three tasks included within 
the image processing stage in a unified approach: brain tissue segmentation in 
diffusion space (\autoref{sec:dwi_segmentation}), correction of geometrical 
distortions (\autoref{sec:distortion}), and structural image registration to 
diffusion coordinate space (\autoref{sec:registration}). These tasks are generally
solved independently, or combined in pairs. However, there exist fundamental 
coupling relationships that can be exploited to obtain a simultaneous solution to 
the three problems. This joint approach satisfactory impacts the downstream
outcomes of the whole pipeline with the increase of the internal consistency.

@@

The last addressed task in the image processing stage of the studied 
connectivity analysis pipelines is the structural information co-registration.
The need for this registration step is mainly raised when defining the 
nodes of the connectivity matrix. This definition step is named
\textit{cortical parcellation} as it imposes the regions that will be
considered to cluster the fiber bundles reaching the \gls{wm}-\gls{gm}
surface. The common procedure to accomplish this clustering is using
a predefined parcellation in a high-resolution structural T1-weighted 
atlas \citep{greve_accurate_2009}. The second goal that has justified the applicability of structural
images co-registration is susceptibility distortion correction
as discussed in \autoref{sec:distortion}. In any case, susceptibility 
distortion hinders a rigid-registration solution to this end.
Additionally, when applying non-linear intensity-based
registration algorithms other difficulties have to be addressed as
the significant \gls{pve} in the \gls{wm}-\gls{gm} layer, or the
inherent inadequacy of the B0 contrast (the only \textit{directionally
independent} existing in the raw \gls{dwi} data) due to the almost null
difference in intensity between \gls{wm} and \gls{gm} pixels. Early 
registration methods appeared targeting the distortion correction.
They quickly standardized the choice of T2 as anatomically correct source
to be registered against the B0 in \gls{dwi}. B0 images have a very similar
contrast to T2 weighted due to the duality of acquisition procedure. However,
parcellation is defined in T1 weighted space, adding an additional registration
step missing on the literature due to the novelty of the task. Even though this
registration step has a very low complexity compared to the remaining tasks of 
the pipeline process, it is one additional source of inconsistency and unreliability.
